---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# prof.tree

[![Travis-CI Build Status](https://travis-ci.org/artemklevtsov/prof.tree.svg?branch=master)](https://travis-ci.org/artemklevtsov/prof.tree) [![Coverage Status](https://img.shields.io/codecov/c/github/artemklevtsov/prof.tree/master.svg)](https://codecov.io/github/artemklevtsov/prof.tree?branch=master)

Provide an alternative profiling data diplay as tree structure.

## Installation

prof.tree is not yet on CRAN; it is currently available from GitHub. Make sure you have the devtools package installed, and then run:

```r
devtools::install_github("artemklevtsov/prof.tree")
```

## Example

```{r}
times <- 4e5
cols <- 150
data <- as.data.frame(x = matrix(rnorm(times * cols, mean = 5), ncol = cols))
data <- cbind(id = paste0("g", seq_len(times)), data)
Rprof(tmp <- tempfile())
data1 <- data   # Store in another variable for this run
# Get column means
means <- apply(data1[, names(data1) != "id"], 2, mean)
# Subtract mean from each column
for (i in seq_along(means))
    data1[, names(data1) != "id"][, i] <- data1[, names(data1) != "id"][, i] - means[i]
Rprof(NULL)
library(prof.tree)
prof.tree(tmp)
unlink(tmp)
```

## Bug reports

First check the changes in the latest version of the package. Type type into R:

```r
news(package = "prof.tree", Version == packageVersion("prof.tree"))
```

Try reproduce a bug with the latest development version from Git.

To report a bug please type into R:

```r
utils::bug.report(package = "prof.tree")
```

Post the `traceback()` and `sessionInfo()` output also may be helpful.
